\documentclass[12pt]{article}
\usepackage{mathtools,amssymb}
\usepackage{enumitem}
\usepackage{fullpage}
\usepackage{fancyvrb}
\usepackage{parskip}


\begin{document}
\thispagestyle{empty}

\begin{center} \bfseries
  \Large IMO Stream Test 4
  \\ \bigskip
  \large April Camp 2025
  \\ \bigskip
  Time: $4\frac{1}{2}$ hours
\end{center}

\bigskip\bigskip
\begin{enumerate}[leftmargin=0pt,itemsep=\bigskipamount]

% A2
\item Let $n$ be a positive integer.
Find the minimum possible value of
\[2^0x_0^2 + 2^1x_1^2 + \dotsb + 2^{n}x_{n}^2\]
where $x_0,x_1,\dotsc,x_{n}$ are nonnegative integers such that $x_0 + x_1 + \cdots + x_{n} = n$.

% C3
\item Let $n$ be a positive integer.
There are $n$ coaches and $n$ students at a maths camp sitting at a round table in some order.
Each of the $n$ students wishes to meet with one of the coaches to argue about their mark for a combinatorics problem from an earlier test at the camp, and no two students wish to meet with the same coach.
A student and coach can argue only if they are seated next to each other at the table.
Every ten minutes, one pair of adjacent people swaps places.

Find the minimum number of exchanges of adjacent people such that, regardless of the initial arrangement, every student can argue with the coach they wish to at some time.

% G6
\item Let $ABC$ be an acute triangle with $AB<AC$, and let $\Gamma$ be the circumcircle of $ABC$.
Points $X$ and $Y$ lie on $\Gamma$ so that $XY$ and $BC$ intersect on the external angle bisector of $\angle BAC$.
Suppose the tangents to $\Gamma$ at $X$ and $Y$ intersect at a point $T$ on the same side of $BC$ as $A$, and that $TX$ and $TY$ intersect $BC$ at $U$ and $V$, respectively.
Let $J$ be the centre of the excircle of triangle $TUV$ opposite the vertex $T$.

Prove that $AJ$ bisects $\angle BAC$.

\end{enumerate}


\vfill
% ASCII art
\centering
\scriptsize % size of the art
% Insert ASCII art (in the verbatim env)
\begin{BVerbatim}
                         .-.
                        |/`\\.._
     _..._,,--.         `\ /.--.\ _.-. 
  ,/'  ..:::.. \     .._.-'/    \` .\/ 
 /       ...:::.`\ ,/:..| |(o)  / /o)|
|:..   |  ..:::::'|:..  ;\ `---'. `--'
;::... |   .::::,/:..    .`--.   .:.`\_
 |::.. ;  ..::'/:..   .--'    ;\   :::.`\
 ;::../   ..::|::.  /'          ;.  ':'.---.
  `--|    ..::;\:.  `\,,,____,,,/';\. (_)  |)
     ;     ..::/:\:.`\|         ,__,/`;----'
     `\       ;:.. \: `-..      `-._,/,_,/
       \      ;:.   ). `\ `>     _:\
        `\,  ;:..    \ \ _>     >'
\end{BVerbatim}

\end{document}