\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{enumitem}
\usepackage{fullpage}

\pagestyle{empty}

\begin{document}

\begin{center} \large
    \textbf{Stellenbosch Camp December 2024}
    
    \textbf{Intermediate Section Test 5}
    
    \textbf{Time: \(4\) hours}
\end{center}

\begin{enumerate}[topsep=2\bigskipamount,itemsep=\bigskipamount]
\item Aidan places an integer in each square of an 8-by-8 chessboard oriented with a black square in the top left corner. He numbers the columns $1,2,\ldots,8$ going left to right and the rows $1,2,\ldots,8$ from top to bottom. He notices that the sum of the numbers in the white squares is 23 and the sum of the numbers in the squares in the odd-numbered columns is 40. At that moment, the Naughty Juku swaps the sign of each number on a white square and blindfolds Aidan. Can Aidan now determine the sum of the numbers in the squares in the odd-numbered rows?

\item % Stellenbosch Camp 2005
Suppose that for some $p, q, r, s \in \mathbb{R}$, the roots of the polynomial $x^{4} + px^{3} + qx^{2} + rx + s$ are all positive real numbers. Prove $pr \geqslant 16s$.

\item %India Regional MO
Let $ABC$ be a triangle and $D$ be the midpoint of $BC$. Suppose that the angle bisector of $\angle{ADC}$ is tangent to the circumcircle of triangle $ABD$ at $D$. Prove $\angle{BAC} = 90^{\circ}$.

\item Kerry has 2024 chests in her Minecraft world.
Of the 2024 chests, 1012 are trapped chests that will trigger TNT to blow up the entire room, and the other 1012 contain diamonds and netherite ingots.
Kerry knows which chests are trapped and which contain the loot.
You want to get the loot without blowing up.
To this end, you are allowed to ask Kerry as many questions of the following form as you want.
In each single question, you select three of the chests, and Kerry then replies by choosing two of these chests and stating how many of those two are trapped.
Can you figure out which 1012 chests have the loot?

\item I have $10^{100}+3$ Discord friends and $10^{20000}$ Discord Nitro vouchers.
I give each of my friends
\[\left\lfloor\frac{10^{20000}}{10^{100} + 3}\right\rfloor\]
of the vouchers, and I keep the remaining vouchers to myself.
What is the units (i.e.~rightmost) digit of the number of vouchers that each one of my friends received?

\item Find all solutions to $a^{a+b} = b^{b-a}$ where $a$ and $b$ are positive integers.
\end{enumerate}
\end{document}