\documentclass[12pt]{article}
\usepackage{mathtools,amssymb}
\usepackage{enumitem}
\pagestyle{empty}
\begin{document}
\begin{center} \large
    \textbf{Stellenbosch Camp December 2024}
    
    \textbf{Intermediate Section Test 4}
    
    \textbf{Time: \(2 \frac{1}{2}\) hours}
\end{center}

\begin{enumerate}[topsep=2\bigskipamount,itemsep=\bigskipamount]
\item Can $3^{2025}$ be written as the sum of two squares?
\item Let $x_1,x_2,\dots,x_9$ be positive real numbers such that
$$x_1^2+x_2^2+\dots + x_9^2\geqslant 25.$$
Show that there exist three distinct indices $i$, $j$, and $k$ such that $1 \leqslant i,j,k \leqslant 9$ and $x_i+x_j+x_k \geqslant 5$.
\item Let $ABC$ be a triangle and $\Gamma$ the circle with diameter $AB$. The bisectors of $\angle{BAC}$ and $\angle{ABC}$ intersect $\Gamma$ (also) at $D$ and $E$ respectively and intersect each other at $I$. Let the feet of the perpendicular lines from $I$ onto $BC$ and $AC$ be $F$ and $G$ respectively. Prove that $D$, $E$, $F$, and $G$ are collinear.
\item There are \(2025\) people at a party. Each two people either know each other or do not know each other. Among each four people at the party, at least one knows the other three. We call a person \emph{esteemed} if that person knows everyone else at the party. What is the smallest possible number of esteemed people at the party?
\item Let \(\mathbb{Z}_{> 0} = \{1, 2, 3, \ldots\}\). Let \(f: \mathbb{Z}_{> 0} \rightarrow \mathbb{R}\) be a function such that for each integer \(n \geqslant 2\), there is a prime factor \(p\) of \(n\) such that \(f(n) = f(n/p) - f(p)\). It is given that
\[f(2^{2023}) + f(3^{2024}) + f(5^{2025}) = 2022.\]
Find the value of \(f(2023^{2}) + f(2024^{3}) + f(2025^{5})\).
\end{enumerate}
\end{document}