\documentclass[12pt]{article}
\usepackage{mathtools,amssymb}
\usepackage{enumitem}

\pagestyle{empty}

\begin{document}

\begin{center} \large
    \textbf{Stellenbosch Camp December 2024}
    
    \textbf{Intermediate Section Test 3}
    
    \textbf{Time: \(2 \frac{1}{2}\) hours}
\end{center}

\begin{enumerate}[topsep=2\bigskipamount,itemsep=\bigskipamount]
\item Find all pairs $(a,b)$ of real numbers with $a+b = 1$, which satisfy $(a^2+b^2)(a^3+b^3)=a^4+b^4$.
\item For which values of $n$ is $1! + 2! + 3! + \dots + n!$ a perfect square?
\item Hugo and Jared play the following game. They take turns writing the numbers 1 to 72 on a $8\times 9$ grid of squares. The numbers may be used in any order, but each number can only be used once. Hugo goes first. At the end of the game, Hugo gets a point for every row or column with an odd sum, and Jared gets a point for every row or column with an even sum. The winner is the one with the higher score. Does one of the players always have a winning? If so, who is it and how? 
\item The diagonals $AC$ and $BD$ of a cyclic quadrilateral $ABCD$ intersect at $P$. The circumcircle of the triangle $PDC$ intersects $BC$ at a point $E$, beyond $C$, and intersects $AD$ at a point $F$, beyond $D$. The circumcircle of the triangle $PAB$ intersects $BC$ at a point $H$, between $B$ and $C$, and intersects $AD$ at a point $G$, beyond $A$. Prove that $E$, $F$, $G$, and $H$ lie on the circumference of a circle with centre $P$.
\item Find all pairs \((p, q)\) of prime numbers such that, for some positive integer \(a\), we have
\[p^{2} + 5pq + 4q^{2} = a^{2}.\]
\end{enumerate}
\end{document}