\documentclass[12pt]{article}
\usepackage{mathtools,amssymb,graphicx}
\usepackage{fullpage,parskip}
\usepackage{enumitem}
\usepackage{hyperref}

\pagestyle{empty}

\begin{document}
\begin{center} \bfseries \large
    February Monthly Problem Set

    Due date: 21 February 2025
\end{center}

\bigskip
Submit your monthly problem sets here: \url{https://forms.gle/pZH93Fq95UuABT277}.
You can ask the coaches from the Stellenbosch Camp for hints, but do not ask other people for help or look for help online.

\begin{enumerate}[topsep=\bigskipamount,itemsep=\bigskipamount]
% C
\item % BJ-2018-4
$2025$ people sit around a circular table.
Every hour there is a vote, where each person votes either yes or no.
Each person $X$ obeys the following rule.
On the $n$th hour, if $X$'s vote is the same as that of at least one of the neighbours of $X$, then $X$'s vote will be the same on the $(n+1)$th hour as on the $n$th hour; otherwise, $X$'s vote on the $(n+1)$th hour will be different from $X$'s vote on the $n$th hour.

Prove that, irrespective of how everyone votes on the first hour, there will be an hour after which nobody's vote will ever change.

% N
\item % JM-2019-2
Let $f,g : \mathbb{Z} \to \mathbb{Z}$ be two functions such that $|f(x)| \leqslant |x|$ and $f(3x+4y) = g(2x+5y)$ for all $x,y \in \mathbb{Z}$.
Find the largest possible value of $f(2025)$.

% A
\newcommand*{\parens}[1]{\left(#1\right)}
\item % LB-2019-3
Let $a$, $b$, $m$, and $n$ be positive integers such that $a \neq b$. Show that
\[ \frac{\parens{a-b}\parens{a^2-b^2}\dotsb\parens{a^{m+n}-b^{m+n}}}{\parens{a-b}\parens{a^2-b^2}\dotsb\parens{a^m-b^m} \cdot \parens{a-b}\parens{a^2-b^2}\dotsb\parens{a^n-b^n}} \]
is an integer. 

% G
\item % 2016 Bulgaria JBMO TST 2.2 (Adapted)
The vertices of the pentagon $ABCDE$ lie on a circle in that order.
The points $H_1$, $H_2$, $H_3$, $H_4$ are the orthocentres of the triangles $ABC$, $ABE$, $ACD$, $ADE$ respectively.
Prove that the quadrilateral determined by the four orthocentres is a rhombus if and only if $BE\parallel CD$ or $BC\parallel DE$.

% A
\item Find all functions \(f: \mathbb{R} \rightarrow \mathbb{R}\) such that, for all \(x, y \in \mathbb{R}\), we have
\[f(f(x - y)) = f(x)f(y) - f(x) + f(y) - xy.\]

% G
\item %Turkey MO 2015, P5

Let $ABCD$ be a cyclic quadrilateral whose largest interior angle is $D$. The lines $BC$ and $AD$ intersect at point $E$, and the lines $AB$ and $CD$ intersect at point $F$. A point $P$ is taken inside of quadrilateral $ABCD$ such that $\angle EPD=\angle FPD=\angle BAD$. Let $O$ be the circumcentre of quadrilateral $ABCD$. Line $FO$ intersects the lines $AD$, $EP$, and $BC$ at $X$, $Q$, and $Y$ respectively. If $\angle DQX = \angle CQY$, show that $\angle AEB=90^\circ$.

% N
\item 
Let $a_1, a_2, a_3, a_4$ be integers such that $0 < a_1 \leqslant a_2 \leqslant a_3 \leqslant a_4 < 23$.
Suppose that $23 \mid a_1^n+a_2^n+a_3^n+a_4^n$ for all positive odd integers $n$.
Prove that $a_1+a_4 = a_2+a_3 = 23$.

% C
\item 
Jon is playing a game with $2^{2025}$ buckets arranged in a circle, numbered clockwise in order from $1$ to $2^{2025}$, all of which are empty except for buckets $2024$ and $2025$ which are full of water.
At the start of the game he can choose to fill some of these buckets with water (each bucket is either completely full or completely empty).
He also has two additional buckets in his hands, one of which is full while the other is empty.

After filling some of the buckets in the circle, he is given an integer $k$ from $0$ to $2024$ inclusive. He will then start at bucket $2^k$. At each step,
\begin{itemize}
\item If he is at an empty bucket, then he will replace it with a full bucket from the buckets he has with him, if possible; whereas
\item If he is at a full bucket, then he will replace it with an empty bucket from the buckets he has with him, if possible;
\end{itemize}
and then he will move $2^k$ buckets clockwise along the circle.
If at any step he cannot replace the bucket in this way he loses the game, but if he can continue on forever no matter the value of $k$ then he wins.
Can Jon fill some of the circle's buckets at the start in such a way as to ensure that he will win the game?
\end{enumerate}

\end{document}