\documentclass[12pt]{article}
\usepackage{mathtools,amssymb}
\usepackage{fullpage,parskip}
\usepackage{enumitem}
\usepackage{hyperref}

\pagestyle{empty}

\begin{document}
\begin{center} \bfseries \large
    May Monthly Problem Set

    Due date: 23 May 2025
\end{center}

\bigskip
Submit your monthly problem sets here: \url{https://forms.gle/pZH93Fq95UuABT277}.
You can ask the coaches from the Stellenbosch Camp for hints, but do not ask other people for help or look for help online.

\begin{enumerate}[topsep=\bigskipamount,itemsep=\bigskipamount,leftmargin=0pt]
% G, PP-2010-5
\item $ABCD$ is a rectangle and $X$ is any point on $CB$ produced.
$P$ is a point on $XA$ produced such that $AD$ bisects $\angle PDX$.
Prove that $CP$ bisects $AD$.

% N, MS-2012-1
\item Let $a$ be an integer such that $a = 4k+1$ for some integer $k$, and let $n$ be a positive integer.
Show that the highest power of $2$ that divides $1 +a +a^2 +\dotsb + a^{n-1}$ is the same as the highest power of $2$ that divides $n$.

% A, JM-2019-4
\item Given a circle $C_1$ with radius $1$, consider the sequence $C_1, S_1, C_2, S_2, C_3, S_3, \dotsc$ of alternating circles and squares, each one inscribed in the previous one.
Determine which is first in this sequence, a circle or a square, to have its area smaller than $1/2025$.

% A, HW-2018-1
\item Prove that if $k$ and $n$ are positive integers, then $(4k)^n$ and $(4k)^n+2^n$ have the same number of digits.

% G, DB-2018-1
\item 
Let $G$ be the centroid and $I$ the incentre of a non-equilateral triangle $ABC$.
Prove that $IG$ is parallel to one of the sides of triangle $ABC$ if and only if the side lengths are in arithmetic progression.

% N, The Liam
\item Prove or disprove the following statement: if $p(x)$ is a polynomial with rational coefficients such that for all positive integers $m$ and $n$ we have that
\[ \frac{p(m) +p(m+1) +\dotsb +p(m+n)}{n+1} \quad\text{is an integer}, \]
then $p(x)$ has integer coefficients.

% A, LB-2018-4
\item Find all functions $f : \mathbb{Z} \to \mathbb{Z}$ such that for all $m,n \in \mathbb{Z}$ we have
\[ f(m+n)^2 +f(m-n)^2 -2f(m)^2-2f(n)^2 = 12f(mn). \]

% C, BJ-2019-1
\item 
Let $t$ be a positive integer and consider a $4\times 2024$ grid $G$.
We wish to colour the $1\times 1$ blocks of $G$ with colours numbered $1,2,\dotsc$ with the condition that two blocks are not allowed to share colour $i$ if the distance between them is less than $i+1$.
(Here, the distance between two blocks with centres $(x_1,y_1)$ and $(x_2,y_2)$ is $|x_1-x_2|+|y_1-y_2|$.)
Find the least number of colours needed for such a colouring.
\end{enumerate}

\end{document}