\documentclass[12pt]{article}
\usepackage{mathtools,amssymb,graphicx}
\usepackage{fullpage}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{hyperref}

\pagestyle{empty}

\begin{document}
\begin{center} \bfseries \large
    January Monthly Problem Set

    Due date: 17 January 2025
\end{center}

\bigskip
Submit your monthly problem sets here: \url{https://forms.gle/pZH93Fq95UuABT277}.
You can ask the coaches from the Stellenbosch Camp for hints, but do not ask other people for help or look for help online.

\begin{enumerate}[topsep=\bigskipamount,itemsep=\bigskipamount]
% G
\item % Stellenbosch Camp 2005
Let $\triangle{ABC}$ be right-angled at $C$ with $BC= CA$, and $D$ be a point on the line $BC$ beyond $C$ such that $CD < BC$.
Furthermore, let $E$ be on the segment $AC$ such that $CE=CD$ and let $P, Q, R, S$ be the midpoints of $AB, BD, DE, EA$ respectively.
Prove that $PQRS$ is a square.

% AC
\item Find the number of tuples $(x_1, x_2, \dots, x_{50})$ of real numbers such that $x_1 = 2$, $x_2 = 3$, and for all $i\in \{1,2,\dots,50\}$, we have
$$(x_i+x_{i+1})^2 = (x_{i+1} + x_{i+2})^2,$$
where $x_{51} = x_{1}$ and $x_{52} = x_{2}$.

% A
\item Let \(r\), \(s\), and \(t\) be positive real numbers. Show that
\[r^{2} + s^{2} + t^{2} + 2rst + 1 \geqslant 2(rs + st + tr).\]

% CG 
% Does not seem free ChatGPT-able nor googlable
\item 
How many ways are there to divide a regular pentagon into 5 triangles of equal area?

% A
\item Let $f: \mathbb{N}_0 \rightarrow \mathbb{R}$ be a function with $f(0) = 0$ such that for all $n \in \mathbb{N}_0$ we have
$$n \leqslant f(n) + f(n+1) \leqslant 2n.$$
\begin{enumerate}[itemsep=0pt]
    \item Show that for all $n \geqslant 2$, we have
    $$|f(2n)| + |f(2n+1)| \leqslant 2n^2.$$
    \item Find all such $f$ such that, for all $n \in \mathbb{N}_{0}$, we have $$|f(2n)| + |f(2n+1)| = 2n^2.$$
\end{enumerate}


% G
\item %Kazakhstan MO, 2008%
Inside a convex quadrilateral $ABCD$, let $P$ be a point such that $\angle APB=\angle ADP+\angle BCP$ and $\angle APD=\angle ABP+\angle DCP$.
Prove that $$AP\cdot CP+BP\cdot DP \geqslant \sqrt{AB\cdot BC\cdot CD\cdot DA}.$$

%C
%Does not seem free ChatGPT-able nor googlable
%You and six of your mathematician friends
\item
Jon Kariv is playing a game with six friends.
Each of the seven people has a coloured sticky note placed on their back.
Each of them can see the sticky note on everyone else but cannot see their own.
There were two more sticky notes but they were hidden and no one was told their colours.
In total there were three red, three yellow, and three green sticky notes, and everyone knows this.
Jon's friends state the following statements one after another.
\begin{itemize}
\item First: ``I don't know the colour of my sticky note.''
\item Second: ``I also don't know my sticky note's colour.''
\item Third: ``I also don't know my sticky note's colour.''
\item Fourth: ``I have deduced that mine is red.''
\item Fifth: ``I have yet to deduce what the colour of mine is.''
\item Sixth: ``I have deduced that my sticky note is yellow.''
\end{itemize}
None of them are colour blind and are all perfectly logical.
Can you determine what colour Jon's sticky note is?

% N
\item % Vietnam MO 1992
Let $n$ be a positive integer.
Let $f(n)$ be the number of divisors of $n$ that end with the digit 1 or 9, and let $g(n)$ be the number of divisors of $n$ that end with the digit 3 or 7.
Prove that $f(n) \geqslant g(n)$.

\end{enumerate}
\end{document}