\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{fullpage}
\usepackage{enumitem}
\pagestyle{empty}

\begin{document}
\begin{center} \large
    \textbf{Stellenbosch Camp December 2024}
    
    \textbf{Advanced Section Test 5}
    
    \textbf{Time: \(4\) hours}
\end{center}

\begin{enumerate}[topsep=2\bigskipamount,itemsep=\bigskipamount]
\item I have $10^{100}+3$ Discord friends and $10^{20000}$ Discord Nitro vouchers. I give each of my friends
\[\left\lfloor\frac{10^{20000}}{10^{100} + 3}\right\rfloor\] of the vouchers, and I keep the remaining vouchers to myself. What is the units (i.e., rightmost) digit of the number of vouchers that each one of my friends received?

\item Find all solutions to $a^{a+b} = b^{b-a}$ where $a$ and $b$ are positive integers.

\item There are 47 students in a classroom with 47 seats, all arranged in one row. 
An adjustment is made to student seats in the new school term.
For a student with the original seat $i$, if their new seat is $m$, we say that the student has moved a distance of $|m-i|$.
Let $S$ denote the sum of all the movement distances of the students. Determine the greatest possible value of $S$.

\item Let $ABCD$ be a square inscribed in circle $\Omega$, and let $P$ be a point on the minor arc $AB$ of $\Omega$.
The lines $PC$, $PD$ meet the diagonals $BD$, $AC$ at points $E, F$ respectively. The lines $AE, BF$ meet the lines $PD, PC$ at points $S, T$ respectively. The points $K, L$ are the projections of $S, T$ respectively to $AB$, and $Q$ is the common point of lines $KT$ and $LS$. Prove that the line $PQ$ bisects the segment $OM$, where $M$ is the midpoint of side $CD$ and $O$ is the centre of $\Omega$.

\item Find all polynomials of the form
\[P(x) = x^{n} + \sum_{i = 0}^{n - 1}a_{i}x^{i} = (x - r_{1})(x - r_{2})\cdots(x - r_{n})\]
where $n \geqslant 1$, the numbers $r_{1}, r_{2}, \ldots, r_{n}$ are real numbers, and each of $a_{n - 1}, a_{n - 2}, \ldots, a_{0}$ is in the set $\{-1, 1\}$.

\item Let \(a\), \(b\), and \(c\) be integers such that \((a, b, c) \neq (0, 0, 0)\) and \((|a|, |b|, |c|) \neq (1, 1, 1)\). Prove that
\[\gcd(a - bc, b - ac, c - ab) \mid \gcd(a, b, c)\gcd(a^{2} - 1, b^{2} - 1, c^{2} - 1).\]
\end{enumerate}
\end{document}