\documentclass[12pt]{article}
\usepackage{amsmath,amssymb}
\usepackage{enumitem}
\begin{document}
\begin{center} \large
\textbf{Stellenbosch Camp December 2024}

\textbf{Advanced Section Test 4}

\textbf{Time: \(2 \frac{1}{2}\) hours}
\end{center}

\begin{enumerate}
\item There are \(2025\) people at a party. Each two people either know each other or do not know each other. Among each four people at the party, at least one knows the other three. We call a person \emph{esteemed} if that person knows everyone else at the party. What is the smallest possible number of esteemed people at the party?
\item Let \(\mathbb{Z}_{> 0} = \{1, 2, 3, \ldots\}\). Let \(f: \mathbb{Z}_{> 0} \rightarrow \mathbb{R}\) be a function such that for each integer \(n \geqslant 2\), there is a prime factor \(p\) of \(n\) such that \(f(n) = f(n/p) - f(p)\). It is given that
\[f(2^{2023}) + f(3^{2024}) + f(5^{2025}) = 2022.\]
Find the value of \(f(2023^{2}) + f(2024^{3}) + f(2025^{5})\).
\item Find all triples \((a, b, c)\) such that \(a\), \(b\), and \(c\) are positive integers that satisfy \(2^{a}3^{b} = 5^{c} + 1\).
\item Let \(n\) be a positive integer. Consider paths (possibly self-intersecting) on the lattice grid in the \(xy\)-plane that start at \((0, 0)\) and consist of \(n\) steps where each step is a move either one unit up, one unit down, one unit right, or one unit left. Prove that the number of such paths that end on the line \(y = 0\) is \(\binom{2n}{n}\).
\item Consider acute-angled $\triangle ABC$ with circumcentre $O$. Let ${\ell}_{A}$ be the perpendicular bisector of $OA$ and let ${\ell}_B, {\ell}_C$ be defined similarly. Let $P_{A}$ be the intersection of $\ell_{A}$ and $CB$ and similarly for $P_{B}$ and $P_{C}$. Assuming they exist, show that $P_{A}, P_{B}, P_{C}$ are collinear.
\end{enumerate}
\end{document}